\chapter{Introduction}

\section{Overview of the Internship}
This report documents the work completed during my internship at Vector GmbH. The internship focused on three main tasks: writing unit tests using the Google Test framework, updating the implementation according to MISRA 2012 rules, and automating test report generation using Python. These tasks were critical in enhancing the reliability, safety, and efficiency of the software development process at Vector GmbH.

\section{About Vector GmbH}
Vector GmbH is a leading provider of software tools and components for the development of electronic systems in automobiles and related industries. The company’s tools and solutions support a wide range of processes including model-based development, testing, and integration of software components. With a strong emphasis on quality and innovation, Vector GmbH is at the forefront of automotive software development.

\section{Scope of Work}
During the internship, I was primarily involved in improving the software testing and reporting processes within the company. The work involved implementing unit tests to ensure code reliability, refactoring code to comply with the MISRA 2012 safety standard, and automating the generation of test reports. These tasks not only contributed to the ongoing projects at Vector GmbH but also provided me with valuable experience in applying industry standards and tools in a real-world setting.

\section{Report Structure}
This report is structured into three main sections, each corresponding to one of the tasks undertaken during the internship:
\begin{itemize}
    \item \textbf{Writing Unit Tests Using Google Test Framework:} This section discusses the creation and implementation of unit tests using the Google Test framework, highlighting the challenges faced and solutions implemented.
    \item \textbf{Updating Implementation According to MISRA 2012 Rules:} This section covers the process of updating existing code to adhere to MISRA 2012 guidelines, ensuring compliance with industry safety standards.
    \item \textbf{Test Report Automation Using Python:} This section details the automation of test report generation using Python, focusing on the benefits of automation and the tools used.
\end{itemize}
